---
title: "Analysis of class surveys"
subtitle: "Table 1"
author: "Katie, Priyanka, Naira, Alex, Kaeya, Taneesha"
date: last-modified
published-title: "Updated"
editor: visual
format: html
code-copy: true
execute:
  message: false
  warning: false
  echo: false
  cache: true
---

Use this as a template. Keep the headers and remove all other text. Overall, your report may be quite short. When it is complete, render and then push changes to your team repository.

```{r}
# load any other packages and read data here
library(tidyverse)
```

## Executive summary

Write a one-paragraph abstract summarizing what you did and your findings. It need not be comprehensive; try to highlight the most important or interesting outcomes.

## Data description

Write a brief description of the dataset. Your description should cover how data were obtained, sample characteristics, and measurements taken. It does not need to be exhaustive, but sufficiently detailed to convey a clear high-level understanding of the dataset. You can utilize bullet points or tables if you feel it would help improve clarity.

## Questions of interest

-   **is there a strong correlation between non industry project with any other variable? (Alex + Priyanka)**

-   

-   **cs 9 vs cs 16: vs self rated proficiency level in coding  (Kaeya + Taneesha)**

    -   Separate cs9 and cs 16

    -   

-   **People who have domain specialization do they have more domains of interests. - Katie and Naira**

## Findings

Summarize your results. Don't try to explain every step you took; focus instead on providing the main data analytic outputs -- tables and figures -- and explaining clearly what they show. Clarify any important decisions you made in obtaining them. You can display codes if you like but it is not necessary.

## Useful tips (remove this section)

Due to the visual editor, most common needs for authoring can be met using menu items in the RStudio IDE. For a comprehensive guide to Quarto, see the [documentation](https://quarto.org/docs/guide/); consult the documentation for anything you can't sort out in the IDE.

### Code chunks

Insert code chunks using the *Insert* drop-down menu or `ctrl + alt + I` . By default in this document, codes will not be shown but results will. If you want to change this behavior, add the chunk option `echo: true` as below.

```{r}
#| echo: true
my_df <- tibble(animal = c('snake', 'gecko'),
                threatening = c(TRUE, FALSE))

my_df
```

Code chunks will be executed in order when the document is rendered, so packages should be loaded at the very beginning of the document

### Rendering tables in markdown

Several functions exist for converting dataframes to markdown tables for nice display. A simple one from the `knitr` package is `knitr::kable()` .

```{r}
my_df %>% knitr::kable()
```

### Figures

To include any figures not generated by code chunks, use *Insert \> Figure / Image* or `![CAPTION](path/file.ext)` .

Most of the time code chunks producing plots will render fine. However, to adjust sizing or alignment, use the chunk options `fig-width` and `fig-height` . Captions can be added with `fig-cap` .

```{r}
#| fig-width: 4
#| fig-height: 3
#| fig-align: left
#| fig-cap: A terrible plot.

my_df %>% 
  ggplot(aes(x = animal, y = threatening)) + 
  geom_col()
```

### Links

To include any hyperlinks, use `[display text](url)` .
