title: "Analysis of class surveys"
subtitle: "Table 1"
author: "Katie, Priyanka, Naira, Alex, Kaeya, Taneesha"
date: last-modified
published-title: "Updated"
editor: visual
format: html
code-copy: true
execute:
  message: false
  warning: false
  echo: false
  cache: true


Use this as a template. Keep the headers and remove all other text. Overall, your report may be quite short. When it is complete, render and then push changes to your team repository.

```{r}
# load any other packages and read data here
library(tidyverse)
```

## Executive summary

Write a one-paragraph abstract summarizing what you did and your findings. It need not be comprehensive; try to highlight the most important or interesting outcomes.

## Data description

Write a brief description of the dataset. Your description should cover how data were obtained, sample characteristics, and measurements taken. It does not need to be exhaustive, but sufficiently detailed to convey a clear high-level understanding of the dataset. You can utilize bullet points or tables if you feel it would help improve clarity.

## Questions of interest

We sought to understand the relationship between coursework and a student's proficiency/curiosity. Our analysis addressed three questions:

1.  Does there exists a relationship between student's preference for non-industry projects and any other variables.
2.  Does taking CMPSC 9 (**Intermediate Python Programming**) versus CMPSC 16 (**Problem Solving with Computers I**) has any relation to self rated proficiency level in coding?
3.  Do people who have done research have more or less domains of interest compared to people who have not done research?

## Findings

Summarize your results. Don't try to explain every step you took; focus instead on providing the main data analytic outputs -- tables and figures -- and explaining clearly what they show. Clarify any important decisions you made in obtaining them. You can display codes if you like but it is not necessary.

## Useful tips (remove this section)

Due to the visual editor, most common needs for authoring can be met using menu items in the RStudio IDE. For a comprehensive guide to Quarto, see the [documentation](https://quarto.org/docs/guide/); consult the documentation for anything you can't sort out in the IDE.

### Code chunks

Insert code chunks using the *Insert* drop-down menu or `ctrl + alt + I` . By default in this document, codes will not be shown but results will. If you want to change this behavior, add the chunk option `echo: true` as below.

```{r}
#| echo: true
my_df <- tibble(animal = c('snake', 'gecko'),
                threatening = c(TRUE, FALSE))

my_df
```

Code chunks will be executed in order when the document is rendered, so packages should be loaded at the very beginning of the document

### Rendering tables in markdown

Several functions exist for converting dataframes to markdown tables for nice display. A simple one from the `knitr` package is `knitr::kable()` .

```{r}
my_df %>% knitr::kable()
```

### Figures

To include any figures not generated by code chunks, use *Insert \> Figure / Image* or `![CAPTION](path/file.ext)` .

Most of the time code chunks producing plots will render fine. However, to adjust sizing or alignment, use the chunk options `fig-width` and `fig-height` . Captions can be added with `fig-cap` .

```{r}
#| fig-width: 4
#| fig-height: 3
#| fig-align: left
#| fig-cap: A terrible plot.

my_df %>% 
  ggplot(aes(x = animal, y = threatening)) + 
  geom_col()
```

### Links

To include any hyperlinks, use `[display text](url)` .
